Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
word choice

A fleet reactor archetype was created for Cyclus.  Although the modeling of
individual, discrete facilities was a motivation for Cyclus, its flexibility
makes it relatively straightforward to create plug-in archetypes to model
anywhere along the spectrum from individual, discrete facilities to
continuous flow fleet facilities.  In order to contrast well with individual,
single-facility granularity modeling, the fleet archetype created here falls more
toward the aggregate, continuous flow side of the spectrum.

>>>>

A fleet reactor archetype was created for Cyclus.  Although the modeling of
individual, discrete facilities was a motivation for Cyclus, its flexibility
makes it relatively straightforward to create plug-in archetypes to model
anywhere along the spectrum from individual, discrete facilities to
continuous flow fleet facilities.  In order to contrast well with the individual,
single-facility granularity modeling that is part of the standard Cyclus archetypes, 
a fleet archetype was created for this work with aggregate facilitiy behavior and
continuous flow.
